---
title: "getting-social-media-handles"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{getting-social-media-handles}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

---
title: "socialmediahandles"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{socialmediahandles}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r eval = FALSE}
if (!require(devtools)) install.packages("devtools")

devtools::install_github("snfagora/MapAgora")
library(MapAgora)
```

This vignette a quick tutorial on how to utilize website data.

## Intro

In the study of organizational and civic life, it is helpful to investigate the public presence of organizations. However, there is no standard way of identifying the social media handles belonging to a given organization. 

Here we approach this problem by extracting social media handles from an organization's website. As a secondary strategy, we also provide the functionality to search for social media handles using the Bing search API.

## Twitter handle

Twitter handles are identified on a page by first extracting all links on the page and then filtering for possible Twitter handles. Some link cleanup is attempted before returning a handle if one can be found. 

```{r, eval=FALSE}
## get MoveOn's twitter handle
tw_handle <- find_twitter_handle_from_org_page("https://moveon.org")
```

## Facebook page

The `find_facebook_page_from_org_page` function works similarly but looks for a Facebook page instead of a handle. 

```{r, eval=FALSE}
## get MoveOn's Facebook page
fb_page <- find_facebook_page_from_org_page("https://moveon.org")
```
